---
title: "CSE 6242 Assignment 1"
author: Vincent La (Georgia Tech ID - vla6)
date: September 3, 2017
output: pdf_document
---

```{r}
# Assignment 1: http://cse6242.gatech.edu/fall-2017/hw1/
# To compile R Markdown in terminal run: Rscript -e "rmarkdown::render('hw1.Rmd', clean=TRUE)"
# To create zip file: zip hw1.zip hw1.Rmd hw1.pdf

require(ggplot2)
require(rmarkdown)

options(expressions=500000)
```

# Question 1: Getting Familiar with R

Below is a code snippet where I print hello world, and also run some code examining factor type. One thing I learned is how to work with factor types in R and how to set an ordered factor. See the `get_familiar_with_r` function defined below. In the example below, I create a factor variable with four levels: summer, fall, winter, and spring, and ordered them.

```{r question1}
get_familiar_with_r <- function(){
	#' This function is for the first part of assignment 1
	#' Run some code examples and observe results
	#' Briefly describe one insight you learned about R in your observations
	#' Illustrate with a sample code snippet and observed output

	# Hello World in R
	print('hello world')

	# Display data sets in ggplot 2 library
	# print(data(package = 'ggplot2'))

	# Working with factors
	current.season = factor('summer',
			  levels = c('summer', 'fall', 'winter', 'spring'),
			  ordered = TRUE) # Ordered factor
	print(current.season)
	print(levels(current.season))

	print('goodbye world')
}
get_familiar_with_r()
```

# Question 2: Log Gamma (Loop Implementation)

```{r question2}
log_gamma_loop <- function(n){
	#' Computes and returns the natural logarithm of the gamma value of a positive integer
	#' using an iterative loop
	#' log gamma is defined as ln((n-1)!) = ln(n-1) + ln(n-2) + ... + ln(1)

	sum = 0
	for (i in seq(n - 1, 1, by = -1)) {
		sum = sum + log(i)
	}
	return(sum)
}
log_gamma_loop(5)
```

# Question 3: Log Gamma (Recursive)

```{r question3}
log_gamma_recursive <- function(n){
	#' Computers and returns the natural logarith mof the gamma value of a positive integer
	#' using recursion
	#' log gamma is defined as ln((n-1)!) = ln(n-1) + ln(n-2) + ... + ln(1)

	# Can stop at n == 2 since n-1 = 1 and log(1) equals 0
	if (n == 2){
		return(0)
	} else {
		sum = log(n - 1) + log_gamma_recursive(n - 1)
		return(sum)
	}
}
log_gamma_recursive(5)
```

# Question 4: Sum of Log Gamma

```{r question4}
sum_log_gamma_loop <- function(n){
	#' Uses log_gamma_loop defined above to sum the log Gamma results over
	#' the range 1 to n
	sum = 0

	# Start at 2 because log(1 - 1) is undefined
	for (i in seq(2, n, by=1)) {
		sum = sum + log_gamma_loop(i)
	}
	return(sum)
}


sum_log_gamma_recursive <- function(n){
	#' Uses log_gamma_recursive defined above to sum the log Gamma results over
	#' the range 1 to n
	sum = 0

	# Start at 2 because log(1 - 1) is undefined
	for (i in seq(2, n, by=1)) {
		sum = sum + log_gamma_recursive(i)
	}
	return(sum)
}

sum_log_gamma_loop(5)
sum_log_gamma_recursive(5)
```

# Question 5: Compare Results to Built-In R Function

```{r question5}
sum_lgamma <- function(n){
	#' Uses built in R function lgamma(n) to sum the log Gamma results over the
	#' range 1 to n
	sum = 0

	# Start at 2 because log(1 - 1) is undefined
	for (i in seq(2, n, by=1)) {
		sum = sum + lgamma(i)
	}
	return(sum)
}
sum_lgamma(5)
```

Next, we draw a graph using `ggplot2` to make comparisons between different methods. For better consistency, we repeat each implementation 1000 times. We then loop over values of n from n = 1 to 30.

```{r drawcomparisons}
make_comparisons <- function(n) {
	#' Compare the execution times of the three implementations of finding the
	#' sum of log gamma defined above
	#' Replicate num_runs times for better consistency

	num_runs = 1000

	gamma_loop = vector('numeric', n - 1)
	gamma_recursive = vector('numeric', n - 1)
	lgamma = vector('numeric', n - 1)
	for (i in seq(2, n, by=1)){
		gamma_loop[i - 1] = system.time(replicate(num_runs, sum_log_gamma_loop(i)))[1]
		gamma_recursive[i - 1] = system.time(replicate(num_runs, sum_log_gamma_recursive(i)))[1]
		lgamma[i - 1] = system.time(replicate(num_runs, sum_lgamma(i)))[1]
	}

	index = c(seq(1, n-1), seq(1, n-1), seq(1, n-1))
	times = c(gamma_loop, gamma_recursive, lgamma)
	method = c(rep('gamma_loop', n-1), rep('gamma_recursive', n-1), rep('lgamma', n-1))

	# To plot: https://stackoverflow.com/questions/13837565/how-to-plot-one-variable-in-ggplot
	df = data.frame(index=index, times=times, method=method)
	ggplot(df, aes(x=index, y=times)) + 
		geom_point(aes(color=method, shape=method, group=method)) +
		xlab('n') + 
		ylab('Time to Execute (1000 times)')
}


make_comparisons(30)
```

Looks like Loop approach performs the worst. Recursive approach performs better, but the built in R function performs the best.