---
title: "CSE 6242 Activity 2"
author: Vincent La (Georgia Tech ID - vla6)
date: September 24, 2017
output:
  pdf_document:
    pandoc_args: [
  "--output=ac2.pdf"
    ]
---

```{r datacleaning, echo=FALSE, results='hide',message=FALSE}
# Activity 2: http://cse6242.gatech.edu/fall-2017/ac2/
# To compile R Markdown in terminal run: Rscript -e "rmarkdown::render('ac2.Rmd', clean=TRUE)"
log_factorial <- function (n) {
    # Return the log of factorial(n) for any integer n > 0
    if (n <= 1)
        return (0)
    return (log(n) + log_factorial(n - 1))
}

sum_log_factorial <- function (n) {
    # Return the sum of log_factorial(i) for i in 1..n
    sum <- 0
    for(i in seq(1, n, 1)) {
        sum <- sum + log_factorial(i)
    }
    return (sum)
}

fibonacci <- function(n) {
    # Return nth Fibonacci number
    if (n <= 1)
        return (n)
    return (fibonacci(n - 1) + fibonacci(n - 2))
}
```

The time complexity of each function is

1. `log_factorial`: $O(n)$
    1. We can see this because in this implementation, for each value of n, the recursive call simply evaluates at n-1, continuing until n = 1.

2. `sum_log_factorial`: $O(n^2)$
    + We can see this because `log_factorial` is $O(n)$ and this implementation of `sum_log_factorial` calls `log_factorial` for each value of $n$.

3. `fibonacci`:  $O(2^n)$
    + We can see this if we draw the recursion tree. When calling `fibonacci(n)`, both `fibonacci(n)` and `fibonacci(n-1)` are called once. However, `fibonacci(n-2)` is called twice. `fibonacci(n-3)` is called four times, etc.
    
```{r fib, fig.height=3, fig.width=3, fig.align='center'}
require(ggplot2)

# Plotting Fibonacci separately since run time takes the longest.
n = seq(1, 35, 1)
method = rep('fibonacci', length(n))
times = c()
for(i in n){
  times = c(times, system.time(fibonacci(i))[1])
}

df = data.frame(index=n, times=times, method=method)

ggplot(df, aes(index, times)) +
  geom_point() +
  xlab('n') +
  ylab('Time to Execute')
```

```{r logfactorial, fig.height=3, fig.width=6, fig.align='center'}
# Testing
n = seq(1, 500, 10)
method = c(rep('log_factorial', length(n)), rep('sum_log_factorial', length(n)))
times = c()
for(i in n){
  times = c(times, system.time(replicate(25, log_factorial(i)))[1])
}

for(i in n){
  times = c(times, system.time(replicate(25, sum_log_factorial(i)))[1])
}

n = c(n, n)
df = data.frame(index=n, times=times, method=method)

ggplot(df, aes(index, times)) +
  geom_point(aes(color=method, shape=method, group=method)) +
  xlab('n') +
  ylab('Time to Execute (100 Runs)')
```
