---
title: "CSE 6242 Activity 5"
author: Vincent La (Georgia Tech ID - vla6)
date: November 27, 2017
output:
  pdf_document:
    pandoc_args: [
    "--output=ac5.pdf"
    ]
---

# Introduction
We will use the `igraph` package to visualize the graph data set.

The name of the Graph data is "Road networks" taken from the Stanford Large Network Dataset Collection. Specifically we will be analyzing the "California road network" (http://snap.stanford.edu/data/roadNet-CA.html). In this graph dataset, intersections and endpoints are represented by nodes and the roads connecting these intersections are represented by undirected edges. 

# Exploring The Graph Dataset

```{r}
# Activity 3: http://cse6242.gatech.edu/fall-2017/ac5/
# To create zip file: zip ac5.zip ac5.Rmd ac5.pdf
require(igraph)
require(ggplot2)

setwd("~/git/GeorgiaTech/cse6242/activity_5")

ca_road_net <- read.table("roadNet-CA.txt")
ca_road_net <- graph.data.frame(ca_road_net)

# Number of edges
num_edges = ecount(ca_road_net)
num_vertices = vcount(ca_road_net)

# Looking at distribution of Degrees of Vertices
# Degree Distribution starts at 0 degrees
max_degree = length(degree_distribution(ca_road_net)) - 1
degrees = 0:max_degree
distribution_df = data.frame(degrees=degrees, pmf=degree_distribution(ca_road_net))
ggplot(distribution_df, aes(x=degrees, y=pmf)) +
  geom_point() +
  ggtitle('Distribution of Degrees of Vertices')

print(degree_distribution)
```

We plot the distribution of degrees of vertices above. Notice that the modal (and median in this case) degrees is 6, which is interesting. 

# Visualizing a part of the Graph

In the next part, we visualize a section of the graph (too big to visualize the entire thing). 

```{r}
ca_road_net.copy <- delete.vertices(ca_road_net, which(degree(ca_road_net) != 10))
plot(ca_road_net.copy)
```
