\documentclass[12pt]{article}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amsmath, amsthm}
\usepackage{booktabs}
\RequirePackage[colorlinks]{hyperref}
\usepackage[lined,boxed,linesnumbered,commentsnumbered]{algorithm2e}
\usepackage{xcolor}
\usepackage{listings}
\lstset{basicstyle=\ttfamily,
  showstringspaces=false,
  commentstyle=\color{red},
  keywordstyle=\color{blue}
}

% Margins
\topmargin=-0.45in
\evensidemargin=0in
\oddsidemargin=0in
\textwidth=6.5in
\textheight=9.0in
\headsep=0.25in

\linespread{1.1}

% Commands
\newenvironment{solution}
  {\begin{proof}[Solution]}
  {\end{proof}}

\title{CSE6250: Big Data Analytics in Healthcare \\ Homework 5}
\author{YOUR NAME (GTID: XXXXXXXXX)}
\date{\today}

\begin{document}

\maketitle

\section{Epileptic Seizure Classification}

\subsection*{1.2 Multi-layer Perceptron}
~

\textbf{b.} Calculate the number of "trainable" parameters in the model with providing the calculation details. How many floating-point computation will occur when a new single data point comes in to the model? [5 points]

\bigskip

\textbf{c.} Attach the learning curves for your MLP model in your report. [2 points]

\bigskip

\textbf{d.} Attach the confusion matrix for your MLP model in your report. [2 points]

\bigskip
\textbf{e.} Explain your architecture and techniques used. Briefly discuss about the result with plots. [3 points]

\subsection*{1.3 Convolutional Neural Network (CNN)}
~

\textbf{b.} Calculate the number of "trainable" parameters in the model with providing the calculation details. How many floating-point computation will occur when a new single data point comes in to the model? [5 points]

\bigskip

\textbf{c.} Plot and attach the learning curves and the confusion matrix for your CNN model in your report. [2 points]

\bigskip
\textbf{d.} Explain your architecture and techniques used. Briefly discuss about the result with plots. [3 points]

\subsection*{1.4 Recurrent Neural Network (RNN)}
~
\textbf{b.} Calculate the number of "trainable" parameters in the model with providing the calculation details. How many floating-point computation will occur when a new single data point comes in to the model? [5 points]

\bigskip

\textbf{c.} Plot and attach the learning curves and the confusion matrix for your RNN model in your report. [2 points]

\bigskip

\textbf{d.} Explain your architecture and techniques used. Briefly discuss about the result with plots. [3 points]

\section{Mortality Prediction with RNN}

\subsection*{2.3 Building Model}
~

\textbf{b.} Explain your architecture and techniques used. Briefly discuss about the result with plots. [5 points]


\end{document}
